Using numerical modelling to investigate temperature and wave exposure as drivers

### 2019-08-30 morphology_paper.Rmd
commit before testing of inclusion of wave power map
updated pdf output for literature review, commited minor changes to rmd file and added to frontiers of marine science pdf template to the 'markdown' folder

```{r wave power map, echo=FALSE, eval= FALSE, fig.cap='\\label{fig:wave power map}Wave power map'}

@@

```{r FB spectrum, echo=FALSE, eval= FALSE, fig.cap='\\label{fig:FB spectrum}Wave power map'}

>>>>

```{r wave power map, echo=FALSE, eval= TRUE, fig.cap='\\label{fig:wave power map}Wave power map'}

@@

```{r FB spectrum, echo=FALSE, eval= TRUE, fig.cap='\\label{fig:FB spectrum}Wave power map'}
